% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}
	\project
	{Money Jar}{- a React Progressive Web App}{2018}
	{\website{https://jars.karrui.me}{https://jars.karrui.me} \github{karrui/money-jar-web} }
	{A sharable, online "money" jar progressive web application to keep track of contributions and how far one is from their goals. Built with TypeScript, using React as the front end and Firebase as the backing database. Hosted with Netlify.}
	{React, TypeScript, Firebase, Netlify}

	\project
	{Taskrr}{- an Express Web App}{2018}
	{\github{karrui/taskrr}}
	{A task matching web application where users can put out tasks they need done, and other users can bid for the right to complete those tasks (Think Fiverr or Taskrabbit). Used to be hosted on DigitalOcean, but has since been decommissioned.}
	{JavaScript, PostgreSQL, Express, DigitalOcean}

	\project
	{Chope God}{- an iOS App}{2018}
	{\infos{Hack \& Roll 2018 Hackathon "Top 8" Winner}}
	{An iOS application hackathon submission for Hack \& Roll 2018. Use Apple’s ARKit to reserve seats at a meeting room or table by marking the spot with an AR pin.  Firebase was used as the backing database to store coordinates of the dropped "pins".}
	{Swift, Firebase}

	\project
	{iungo}{- a Java Desktop App}{2017}
	{\github{CS2103AUG2017-F11-B3/main}}
	{A Java desktop address book application controlled using a command line-like interface, with GUI by JavaFX. Also achieved test coverage of 90\% with JUnit.}
	{Java, JavaFX, JUnit 4}

\end{projects}
