% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}
\begin{center}
	More of my projects can be found on my website, \website{https://karrui.dev}{karrui.dev}
\end{center}

\begin{projects}
	\project
	{CAP Calculator}{- a React TypeScript Web App}{2018}
	{\website{https://cap.karrui.dev}{cap.karrui.me} \github{karrui/cap-calculator} }
	{A TypeScript React application for NUS undergraduates to calculate their current CAP (Cumulative Average Point), helping them to visualize what grades are needed to hit their goal, or what their current grade is.}
	{React, TypeScript, Firebase, Netlify}
	\project
	{Static Program Analyser for SIMPLElang}{- a C++ Desktop App}{2018}
	{\infos{Code privatised (due to school policy) but available on request}}
	{A C++11 desktop static program analyser application. Worked extensively on the tokenizer and the parser for parsing the given input source code. Made sure code followed design principles such as Open-Closed Principle. Wrote unit, integration and system tests using equivalence partitioning.}
	{C++}
	\project
	{Money Jar}{- a React TypeScript Web App}{2018}
	{\website{https://jars.karrui.dev}{jars.karrui.me} \github{karrui/money-jar-web} }
	{A sharable, online "money" jar progressive web application to keep track of contributions and how far one is from their goals. Built with TypeScript, using React as the front end and Firebase as the backing database. Hosted with Netlify.}
	{React, TypeScript, Firebase, Netlify}
	\project
	{Chope God}{- an iOS App}{2018}
	{\infos{Hack \& Roll 2018 Hackathon "Top 8" Winner}}
	{An iOS application hackathon submission for Hack \& Roll 2018. Use Apple’s ARKit to reserve seats at a meeting room or table by marking the spot with an AR pin.  Firebase was used as the backing database to store coordinates of the dropped "pins".}
	{Swift, Firebase}
	% \project
	% {iungo}{- a Java Desktop App}{2017}
	% {\github{CS2103AUG2017-F11-B3/main}}
	% {A Java desktop address book application controlled using a command line-like interface, with GUI by JavaFX. Also achieved test coverage of 90\% with JUnit.}
	% {Java, JavaFX, JUnit 4}
\end{projects}
